Plastic in the Urban Freshwater Environment

### 2021-11-29 code/processing_code/map_images.Rmd
improve manuscript map

ggsave(map_grid, filename = here("results", "map_grid.png"))
```

>>>>

ggsave(map_grid, filename = here("results", "map_grid.png"))

map_grid1 <- grid.arrange(rasterGrob(map_fall), rasterGrob(map_winter), ncol = 2)
ggsave(map_grid1, filename = here("results", "map_grid1.png"))
map_grid2 <- grid.arrange(rasterGrob(map_spring), rasterGrob(map_summer), ncol = 2)
ggsave(map_grid2, filename = here("results", "map_grid2.png"))
```

### 2021-11-29 products/manuscript/Manuscript.Rmd
improve manuscript map

```{r map-grid,  fig.cap='Seasonal Maps of Microplastic Concentration', echo=FALSE}
knitr::include_graphics("../../results/watershed_overtime.png")
```

>>>>

```{r map-grid,  fig.cap='Seasonal Maps of Microplastic Concentration', echo=FALSE, fig.height=3}
knitr::include_graphics("../../results/map_grid.png")
```
